---
title: "Interpretation of prediction model"
author: "yonggi.yeom"
output: html_document
---

This is the document for New Donor LTV Predict model using Pledge and CS Center data.
<br/><br/><br/>

>### **Prepare the data with data preprocessing**

#### Library Used

```{r library, message=FALSE, warning=FALSE }
library(readxl)
library(dplyr)
library(lubridate)
library(ggplot2)
library(tidymodels)
library(data.table)
library(ranger)
```


#### Data Preprocessing for CS Center Data
You can also get this file from Report Function in Charitable, (Report Number : OP32)   
<br/>

```{r, echo=TRUE, message=FALSE, warning=FALSE}
call <- read_excel("call.xlsx") #Import data

call_sel <- call %>% select(`Serial Number`, `Task Group` ,`Task Closed Date`) # Selected columns 

call_sel <- 
  call_sel %>%
  group_by(`Serial Number`) %>% 
  mutate(count = n()) %>% 
  arrange(desc(`Task Closed Date`)) %>% 
  distinct(`Serial Number`, .keep_all = TRUE) 
#Removed duplicated record by serial No.

call_tran <- 
  call_sel %>% 
  select(`Serial Number`, `Task Closed Date`, count) %>% 
  mutate_if(is.character, as.factor)
#Selected columns again and generated new column
  
call_tran$`Task Closed Date` <- as.numeric(call_tran$`Task Closed Date`)
#Changed column format as numeric

call_tran <- as.data.frame(call_tran)

```

Call data will be used to extract the number of calls and check the correlation with Pledge data.

Prepare the data by using the latest records and creating a "count" column containing the total number of call records.   
<br/>

```{r, echo=FALSE}
glimpse(call_tran)

```

#### Data Preprocessing for Pledge Data
You can also get this file from Report Function in Charitable, (Report Number : OP24)   
<br/>
```{r, echo=TRUE, message=FALSE, warning=FALSE}
new <- read_excel("new.xlsx") #Import data

new_date <- 
  new %>% 
    filter(`Pledge Created` >= as.Date("2023-07-01") & `Pledge Created` <= as.Date("2024-01-31")) %>% 
  filter(Frequency == 1) 
#selected specific period and recurring pledge 

new_sel <- 
  new_date %>% 
  select(SerialNo, DOB, Gender, SourceCode, Bank, TotalContribution, ChannelType, D0, `Pledge Created`, successful_transactions_count, Campaign)
#Selected columns

new_tran <- 
  new_sel %>% 
  mutate(total =TotalContribution) %>% 
  dplyr::select(- TotalContribution) %>% 
  mutate_if(is.character,as.factor)
#Changed Y column name and changed column format

new_tran$DOB <- as.numeric(new_tran$DOB)
new_tran$D0 <- as.numeric(new_tran$D0)
new_tran$`Pledge Created` <- as.numeric(new_tran$`Pledge Created`)
#Changed column format as numeric

```
<br/>

As you know, the pledge data contains lots of data including personal information which has to remove   
<br/>
Data preprocessing was performed by selecting the necessary columns and changing the characteristics of the columns.   
<br/>
For modeling purposes, a factor column containing many values must be converted to characters.   
<br/>
```{r,echo=TRUE, message=FALSE, warning=FALSE}

new_tran <- 
  new_tran %>% 
  mutate(cam = ifelse(is.na(Campaign),0,1)) %>% 
  dplyr::select(-Campaign)

new_tran$cam <- as.factor(new_tran$cam)  
new_tran$SerialNo <- as.character(new_tran$SerialNo)

```
<br/><br/>

#### Changed column for merge data

```{r, echo=TRUE, message=FALSE, warning=FALSE}
setnames(call_tran, old = "Serial Number", new = "SerialNo")
setnames(call_tran, old = "Task Closed Date", new = "task date")

pled <- 
  new_tran %>% 
  left_join(call_tran, by = "SerialNo")
#Merge data.
```
<br/>

#### Check the merged data
<br/>
```{r, echo=FALSE}
glimpse(pled)
```

Replaced "NA" value,
if the column format is numeric then "Na" Value to "0".<br/>
if the column format is character or factor then "Na" value is to "emt" . 

```{r, echo=TRUE, message=FALSE, warning=FALSE}
pled <- 
  pled %>% 
  mutate(task = ifelse(is.na(`task date`),0,`task date`)) %>% 
  mutate(count = ifelse(is.na(count),0,count)) %>% 
  select(-`task date`)

pled <- 
  pled %>% 
  mutate(DOB = ifelse(is.na(DOB),0,DOB)) %>% 
  mutate(D0 = ifelse(is.na(D0),0,D0)) %>% 
  mutate(Gender = if_else(is.na(Gender),"emt",Gender)) %>% 
  mutate(ChannelType = if_else(is.na(ChannelType),"emt",ChannelType)) %>% 
  mutate_if(is.character,as.factor)

pled$SerialNo <-as.character(pled$SerialNo) 
#Serial No. is not used in the model.

```

```{r, echo=FALSE}
skimr::skim(pled)
```

>### **Building a predictive model**

<br/>

#### Split data into “train” and “test”

```{r, }
set.seed(123) #Random number settings

split <- initial_split(pled, prop = 0.7) #7:3
train<- training(split)
test <- testing(split)

```
<br/>

#### Prepare the data for modeling

Preprocessing for modeling, use "receipe" function in "tidymodels"

```{r, echo=TRUE}
rf_recipe_1 <- 
  recipe(total ~ ., data = train) %>%
  step_center(all_numeric_predictors()) %>%      #Centered from the mean
  step_scale(all_numeric_predictors()) %>%       #Scaling by sd
  step_rm(SerialNo) %>%                          #Excluding serial number
  step_zv(all_numeric_predictors()) %>%          #Exclude variables with zero variance (variance is 0 and not predicted)
  step_normalize(all_numeric_predictors())   #normalization

```
<br/>


#### Generating Model with Random Forest
<br/>
```{r}
mty <- rf_recipe_1 %>% 
  prep() %>% 
  bake(new_data = NULL)

#mty value have to follow total independent value contains factor column as well

```

.
<br/>

```{r}
rf_model <- 
  rand_forest(mtry = 3) %>%
  set_engine("ranger") %>%
  set_mode("regression")
```


#### Fit the preprocessing model to "train" and "test" data
<br/>

```{r, echo=TRUE}
pre_train <- rf_recipe_1 %>% prep() %>% bake(new_data = train)
pre_test <- rf_recipe_1 %>% prep() %>% bake(new_data = test)

```

#### Fitting and Training the Model with prepared data 
<br/>
```{r, echo=TRUE}
rf_fit <-   rf_model %>%   fit(total ~ ., data = pre_train)

rf_pred <-   rf_fit %>%   predict(new_data = pre_test)

```


#### Evaluate models with real data.
<br/>
```{r}
com_data <- data.frame(truth = pre_test$total, estimate = rf_pred$.pred)

com_data_tbl <- as_tibble(com_data)

r_squared <- 1 - sum((com_data_tbl$truth - com_data_tbl$estimate)^2) / sum((com_data_tbl$truth - mean(com_data_tbl$truth))^2)

r_squared 
```



